% !TEX program = xelatex

\documentclass{resume}
%\usepackage{zh_CN-Adobefonts_external} % Simplified Chinese Support using external fonts (./fonts/zh_CN-Adobe/)
%\usepackage{zh_CN-Adobefonts_internal} % Simplified Chinese Support using system fonts

\begin{document}
\pagenumbering{gobble} % suppress displaying page number

\name{Wanru Zhao}

\basicInfo{
  \email{zhaowrenee@gmail.com} \textperiodcentered\ 
  \phone{(+86) 188-100-10893} \textperiodcentered\ 
  \github[Ryan0v0]{https://github.com/Ryan0v0}}
\section{\faGraduationCap\ Education}
\datedsubsection{\textbf{Beihang University (BUAA)}, Beijing, China}{2017 -- Present}
\begin{itemize}
  \item  \textit{B.S.} in Computer Science and Engineering (CSCE), expected June 2021
  \item GPA:3.6/4.0 (Top10\%)
\end{itemize}
\datedsubsection{\textbf{Cambridge Summer School}, Cambridge, United Kingdom}{July. 2018 -- Aug. 2018}
\begin{itemize}
  \item  \textit{visiting student} in Downing College
  \item got As in all lessons 
\end{itemize}

\section{\faUsers\ Experience}
\datedsubsection{\textbf{State Key Laboratory of Software Development Environment} Beijing, China}{July. 2019 -- Present}
\role{Summer Intern}{research assistant}
{\textbf{Publication:}{\emph{Graph Attention based Proposal 3D ConvNets for Action Detection,}\textbf{AAAI 2020, submitted}}}\\
{Jun Li, Xianglong Liu, Zhuofan Zong, \textbf{Wanru Zhao}, Minyuan Zhang, Jingkuan Song}

\datedsubsection{\textbf{Crowd Intelligence Lab} Beijing, China}{Apri. 2019 -- Present}
\role{Supervisor: \textbf{A/Prof. Yongxin Tong}}{}
Big Data and Crowd Intelligence
\begin{itemize}
  \item Dynamic pricing in spatial crowdsourcing, cooperating with \textbf{Didi Chuxing Technology Co.} 
  \item Spatio-temporal data processing and analysis
  \item Federated Learning
\end{itemize}
% Reference Test
%\datedsubsection{\textbf{Paper Title\cite{zaharia2012resilient}}}{May. 2015}
%An xxx optimized for xxx\cite{verma2015large}
%\begin{itemize}
%  \item main contribution
%\end{itemize}

\section{\faCogs\ Skills}
\begin{itemize}[parsep=0.5ex]
  \item Programming Languages: C/C++, Java, Python, SQL, Linux Shell, Verilog HDL, Mip Assembly,  \LaTeX
  \item Platform: Windows, Linux, OS X
  \item Software: Matlab, SPSS
\end{itemize}

\section{\faHeartO\ Honors and Awards}
%% Reference
%\newpage
%\bibliographystyle{IEEETran}
%\bibliography{mycite}
%\begin{onehalfspacing}
\datedline{\textit{Bronze Medal}, ACM International Collegiate Programming Contest (ICPC)\\ China Invitational and Silk-Road Contest}{Jun. 2019}
\datedline{\textit{Silver Medal}, ACM China Collegiate Programming Contest (CCPC) - WFinal}{Jun. 2018}
\datedline{\textit{2rd}, Beijing Forestry University Collegiate Programming Contest}{Jun. 2019}
\datedline{\textit{15th}, The 14th Beihang University Collegiate Programming Contest (BCPC)}{Apr. 2019}
\datedline{\textit{the First Prize}, Scholarship for Academic Records of Beihang University}{Jun. 2018}
\datedline{\textit{the Third Prize}, The 28th "Fengru Cup" Competition of Innovation of Beihang University}{Mar. 2018}
\datedline{\textit{Bronze Medal}, CCF National Olympiad in Informatics (NOI)}{Jul. 2016}
\datedline{\textit{the First Prize}, CCF National Olympiad in Informatics in Provinces (NOIp)}{Nov. 2015}
%\end{onehalfspacing}

\section{\faUsers\ Extracurricular Activities}
\begin{itemize}[parsep=0.5ex]
	\item Key member of technology department of Microsoft Student Club (MSC) in BUAA
	\item Key member of Innovation and Entrepreneurship Center in Beihang University Student Union
	\item Keen on Outdoor Sports.  climbed Peak Nochma,Minya Konka (altitude of 5588m)
	\item Keen on art and music. Got the qualification for the grade nine in piano-playing. Got full mark in the elective course offered by Central Academy of Fine Arts
\end{itemize}

\end{document}
